disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-12-03 article.Rnw
Tidy edit
Tidy up plot formatting and add authors

%
<<kintroptions, echo=FALSE>>=
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.width = 7
)
@
%

@@

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Anita K Nandi\\University of Oxford
   \And Tim CD Lucas\\University of Oxford
   \And Rohan Arambepola\\University of Oxford}
   %\AND Andre Python\\University of Oxford
   %\And Daniel J Weiss\\University of Oxford}
\Plainauthor{Anita K Nandi, Tim CD Lucas, Rohan Arambepola, Andre Python, Daniel J Weiss}

@@

%
<<installview, eval=FALSE>>=
devtools::install_github("aknandi/disaggregation")
library(disaggregation)
@
%

@@

%
<<setuppaths>>=
library(raster)

@@

%
<<showdata, dev='png'>>=
summary(dis_data)
plot(dis_data)
@
%

@@

%
<<showmodel>>=
summary(fitted_model)
plot(fitted_model)
@
%

@@

%
<<showpredictions, dev = 'png'>>=
plot(model_predictions$mean_predictions)
plot(model_predictions$uncertainty_predictions)
@

>>>>

%
<<kintroptions, echo=FALSE>>=
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE,
  fig.width = 6,
  fig.height = 4
)
@
%

@@

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Anita K Nandi\\University of Oxford
   \And Tim CD Lucas\\University of Oxford
   \And Rohan Arambepola\\University of Oxford
   \AND Peter Gething\\Telethon Kids Institute \\ Curtin University
   \And Daniel J Weiss\\University of Oxford}
\Plainauthor{Anita K Nandi, Tim CD Lucas, Rohan Arambepola, Andre Python, Daniel J Weiss}

@@

%
<<installview, eval=FALSE>>=
devtools::install.packages("disaggregation")
library(disaggregation)
@
%

@@

%
<<setuppaths, results='hide'>>=
library(raster)

@@

%
<<summarydata>>=
summary(dis_data)
@
%

%
<<plotdata, eval=FALSE>>=
plot(dis_data)
@
%

%
<<plotdatahidden, echo=FALSE, results='hide', fig.show='hide'>>=
data_plots <- plot(dis_data)
@
%

%
<<plotdata1, echo=FALSE, dev='png', fig.width = 8, fig.height = 6>>=
data_plots$polygon
@
%

%
<<plotdata2, echo=FALSE, dev='png', fig.width = 8, fig.height = 5>>=
data_plots$covariates
@
%

%
<<plotdata3, echo=FALSE, dev='png', fig.width = 5, fig.height = 5>>=
INLA::plot.inla.mesh(dis_data$mesh, main = 'INLA mesh for spatial field')
@
%

@@

%
<<summarymodel>>=
summary(fitted_model)
@
%

%
<<plotmodel, fig.width = 10, fig.height = 6>>=
plot(fitted_model)
@
%

@@

%
<<plotmean, dev = 'png', fig.width = 10, fig.height = 7>>=
plot(model_predictions$mean_predictions)
@
%

%
<<plotuncertainty, dev = 'png', fig.width = 10, fig.height = 5>>=
plot(model_predictions$uncertainty_predictions)
@
%
